Development of Performance Regression Analysis Tool using Distributed Tracing on microservice-based Application\\

### 2022-08-24 paper.tex
txs auto checkin

Seeing the needs of the PRA system above, the approach the will be carried out to do performance regression analysis will be Cummulative Analysis and Aggregation Analysis.

>>>>

Seeing the needs of the PRA system above, the approach the will be carried out to do performance regression analysis will be Cummulative Analysis and Aggregation Analysis \cite{parker2020distributed}.
